\documentclass{article}
\usepackage{ragged2e}

\newcommand\tab[1][1cm]{\hspace*{#1}}
\newcommand{\tuta}{\emph{T.~absoluta}}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\setlength{\RaggedRightParindent}{\parindent}

\begin{document}

To: \\
\tab The Editor,\\
\tab Nature Communications
\begin{flushright}
\date[\today
\end{flushright}

\RaggedRight

Dear Editor,
\par
Please find attached for your review the manuscript titled~``A
Multi-pathway Model to Assess the Threat of Invasive Agricultural Pests:
Case Study of \emph{Tuta~absoluta} in Asia", to be considered for possible
publication in Nature Communications.
\par
In this manuscript, we develop an agent-based model to study invasive
species spread capturing self-mediated as well as human-mediated pathways
of spread. It is applied to study the risk of spread of \tuta{} in the
region of South and Southeast Asia, a region at the fronier of its current
range. This pest of tomato has gained a lot of attention in the last decade
since its introduction from South America to Spain in 2006.  This paper is
relevant to Nature Communications both from the perspective of
understanding the dynamics of \tuta{} as well as the modeling methodology.
To the best of our knowledge, this is the first work on \tuta{} which
accounts for vegetable production and trade as a pathway of spread.
\par
This work has not been published in any journal, nor is it currently under
review elsewhere. All authors have seen and approved the manuscript and
have significantly contributed toward the paper. We appreciate your time
and consideration.
\par
Thank you,\\
Abhijin Adiga\\
Research Assistant Professor\\
Biocomplexity Institute of Virginia Tech\\
abhijin@gmail.com, abhijin@vt.edu
\end{document}
